% !TEX root = ./main.reuse.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% An empty LaTeX project with useful packages and commands
%
% First created on: Nov 9, 2019
% Last updated on:  Feb 4, 2025
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\mode{lncs}
\input{core.style}
\input{core.constants}
\input{core.config}
\input{core.include}
\input{core.thm.env}

% TODO: CONFIGURE core.config.tex USING CONSTANTS IN core.constants.tex

% Import extra packages
\usepackage{subfig}
\usepackage{txfonts} % times
\usepackage{lipsum}
\usepackage{adjustbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{core.frontmatter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Example use of todo commands
\todo{Artem}{Briefly discuss the research area of process mining.}
\chat{Artem}{To accomplish this task, read~\cite{PolyvyanyyPQM2022}.}
\chat{Author}{Thanks, I will do that!}
\done{Author}{Briefly discuss the research area of process mining.}

Use the {$\backslash$change\{old text\}\{new text\}} command to track changes in the manuscript like this: \change{old text}{new text}; where ``old text'' is the old text and ``new text'' is the new text.
Use one of the three versions of the command in \texttt{core.config.tex} to suit your purpose.

Use the {$\backslash$blind\{Artem Polyvyanyy\}} command to remove information that would identify the authors of this manuscript when preparing it for a double-blind review like this: \blind{Artem Polyvyanyy}.
Use {$\backslash$blind[Unblinded text]\{Blinded text\}} to seamlessly switch between unblinded and blinded text like this:
\blind[In our previous work~\cite{PolyvyanyyPQM2022}, we showed that \ldots]{Previously, \citet{PolyvyanyyPQM2022} showed that \ldots}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Write an introduction following the ``funnel'' principle; that is, start with general ideas and gradually specify those into concrete contributions. In the first paragraph, introduce the research area. Use this first paragraph to capture the attention of a \emph{broad audience}. If the reader can not relate to the research area, they will most likely stop reading the paper here. In the second paragraph, introduce the \emph{problem}/\emph{research question(s)} tackled in the paper. Then, list the \emph{requirements} ($R1$, $R2$, and $R3$) for the solution to the problem proposed in this paper and discuss why they are reasonable; unrealistic requirements will diminish the value of the contribution. In the third paragraph, clearly state the \emph{contributions} as you, the author(s), understand them; a bullet point list can be an effective way to present the contributions. Emphasize the \emph{novelty} and \emph{usefulness} of the contributions. Finally, in the last paragraph, introduce the structure of the paper by unveiling the content of the subsequent sections.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\label{sec:background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This section should discuss approaches that tackle the same \emph{problem} as your approach but do not address any of the \emph{requirements} ($R1$, $R2$, and $R3$) discussed in the Introduction section.

There is no need to introduce an explicit section entitled ``Background.''
This discussion on the background of your work can be incorporated into other sections, for example, the Introduction and/or Related Work sections.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
\label{sec:related:work}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section, discuss every existing technique that solves the same \emph{problem} as your approach and addresses a subset of the \emph{requirements} ($R1$, $R2$, and $R3$).
For example, you can write: ``The approach by \citet{PolyvyanyyPQM2022} addresses the problem partially; that is, $R1$ and $R2$, but not $R3$.''

You should discuss all important existing solutions to the \emph{problem} your approach solves.
It is ideal if, through the discussions of this section, you identify existing solutions with which you should compare your approach.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivating Example}
\label{sec:motivating:example}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries}
\label{sec:preliminaries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Approach}
\label{sec:approach}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation}
\label{sec:evaluation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{bibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\input{core.reuse.automata}
\input{core.reuse.petri}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\listoftodos
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%